### 2018-08-29 Sections/mathematical_representation_of_quantum_networks.tex
Q map reduce
Added quantum voting, enigma machines
Fixed caption dist

\begin{figure}[!htb]
\includegraphics[width=0.325\textwidth]{example_routes}
\caption{Example of a simple network with multiple routes \mbox{$A\to B$}. Note that $R_3$ and $R_4$ are competing with one another for use of the last link, which the routing strategy, $\mathcal{S}$, will need to resolve if multiple simultaneous transmissions are taking place.} \label{fig:example_routes}
\end{figure}

\begin{figure}[!htb]
\includegraphics[width=0.3\textwidth]{example_opt}
\caption{The same network graph from Fig.~\ref{fig:example_routes}, with links weighted by some arbitrary cost metric. Applying a shortest-path algorithm yields the optimal route between Alice and Bob to be \mbox{$A\to F\to B$}, which incurs a net cost of \mbox{$c=2$}, as opposed to all other routes, which incur a net cost of \mbox{$c=3$}.} \label{fig:simp_route_opt}
\end{figure}

@@

No particular route through a network is going to have infinite capacity, and therefore we cannot typically always reemploy the same most cost-effective route for all data. Particularly in multi-user networks, as routes are employed for communicating quantum states, their cost metrics may change according to load, or other external influences. Alternately, some routes may come into and out of operation. For example, a satellite requiring line-of-sight communication may oscillate in and out of sight, thereby periodically enabling and disabling respective network routes. For this reason, it is important that strategies accommodate dynamic changes in the network. This is easily accounted for by letting the edge weights in our network graph be a function of time, $G_t$, which are updated via the application of a strategy, which may also be time-dependent,
\begin{definition}[Time-dependent routing strategies]
A time-dependent strategy, $\mathcal{S}_t$, updates the network graph, $G_t$, at each time-step $t$,
\begin{align} \label{eq:S_G}
G_{t+1} = \mathcal{S}_t(G_t).
\end{align}
\end{definition}
For example, the network might have bandwidth restrictions on some links, in which case if more than a certain amount of data is transmitted through a link, it is no longer available for use until previous transmissions have completed. Or, based on market dynamics, the dollar cost of utilising a link may change with its demand.

>>>>

\begin{figure}[!htbp]
\includegraphics[width=0.325\textwidth]{example_routes}
\captionspace \caption{Example of a simple network with multiple routes \mbox{$A\to B$}. Note that $R_3$ and $R_4$ are competing with one another for use of the last link, which the routing strategy, $\mathcal{S}$, will need to resolve if multiple simultaneous transmissions are taking place.} \label{fig:example_routes}
\end{figure}

\begin{figure}[!htbp]
\includegraphics[width=0.3\textwidth]{example_opt}
\captionspace \caption{The same network graph from Fig.~\ref{fig:example_routes}, with links weighted by some arbitrary cost metric. Applying a shortest-path algorithm yields the optimal route between Alice and Bob to be \mbox{$A\to F\to B$}, which incurs a net cost of \mbox{$c=2$}, as opposed to all other routes, which incur a net cost of \mbox{$c=3$}.} \label{fig:simp_route_opt}
\end{figure}

@@

No particular route through a network is going to have infinite capacity, and therefore we cannot typically always reemploy the same most cost-effective route for all data. Particularly in multi-user networks, as routes are employed for communicating quantum states, their cost metrics may change according to load, or other external influences. Alternately, some routes may come into and out of operation. For example, a satellite requiring line-of-sight communication may oscillate in and out of sight, thereby periodically enabling and disabling respective network routes. For this reason, it is important that strategies accommodate dynamic changes in the network. This is easily accounted for by letting the edge weights in our network graph be a function of time, $G_t$, which are updated via the application of a strategy, which may also be time-dependent,
\begin{definition}[Time-dependent routing strategies]
A time-dependent strategy, $\mathcal{S}_t$, updates the network graph, $G_t$, at each time-step $t$,
\begin{align} \label{eq:S_G}
G_{t+1} = \mathcal{S}_t(G_t).
\end{align}
$S_t$ could be any \textbf{BPP} algorithm, deterministic or probabilistic.
\end{definition}
For example, the network might have bandwidth restrictions on some links, in which case if more than a certain amount of data is transmitted through a link, it is no longer available for use until previous transmissions have completed. Or, based on market dynamics, the dollar cost of utilising a link may change with its demand.

### 2018-08-29 Sections/models_for_quantum_computation.tex
Added quantum voting, enigma machines
Finished 2 col fig formatting
Fixed caption dist

\begin{figure}[htpb]
	\begin{align}
		\Qcircuit @C=.7em @R=.4em @! {
		\lstick{\ket{\psi_1}} & \qw & \qw & \ctrl{1} & \gate{Y} & \meter & \control \cw\\
		\lstick{\ket{\psi_2}} & \qw & \targ & \ctrl{-1} & \qw & \meter & \cwx\\
		\lstick{\ket{\psi_3}} & \gate{H} & \ctrl{-1} & \qw & \qw & \gate{X} \cwx & \gate{Z} \cwx & \rstick{\ket{\phi}} \qw
		} \nonumber
	\end{align}
	\caption{Simple example of a quantum circuit on 3 qubits, comprising several single- and 2-qubit quantum gates and measurements. Rows represent qubits, and time flows from left-to-right.} \label{fig:eg_circuit}
\end{figure}

@@

\begin{figure}[htpb]
	\includegraphics[width=0.3\textwidth]{cluster_state}
	\caption{Example of a \mbox{$4\times 3$} rectangular lattice cluster state. Each vertex in the graph represents a qubit initialised into \mbox{$\ket{+}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$}. Edges represent the application of CZ gates between qubits (CZ gates commute, so the order is unimportant). Of sufficient dimension, states of this topology enable universal measurement-based quantum computation, whereby computation proceeds purely via single-qubit measurements, and all entangling operations have been commuted to the state preparation stage. Because CZ gates commute, the preparation of cluster states is time-independent, and easily implemented in a distributed or parallelised manner. The time-ordering of the single-qubit measurements is dependent on the structure of the graph and the algorithm.} \label{fig:cluster_state}
\end{figure}

@@

\begin{figure}[htpb]
	\includegraphics[width=0.375\textwidth]{cluster_state_circuit}
	\caption{Simple example of a cluster state that performs a computation comprising single-qubit operations and a CZ gate between two logical qubits. Let the two horizontal chains represent our two logical qubits. After inputting our input state from the left, we progressively measure out the cluster state qubits chronologically from left-to-right. Upon each single-qubit measurement, the choice of measurement basis teleports the action of a single-qubit gate. These accumulate sequentially. When we reach the point of measuring the two cluster state qubits joined with the vertical edge, the logical qubits accumulate the action of a CZ gate between them, since this is identically what that vertical edge physically corresponds to. Reaching the final two qubits, one from the upper rail and one from the lower, we obtain our two output logical qubits.} \label{fig:cluster_state_circuit}
\end{figure}

@@

\begin{figure}[htpb]
	\begin{align}
		\Qcircuit @C=.7em @R=.4em @! {
		\lstick{\ket{\psi}} & \ctrl{1} & \gate{H} & \meter & & \\
		\lstick{\ket{+}} & \ctrl{0} & \qw & \gate{X} \cwx & \gate{H} & \rstick{\ket\psi} \qw \\
		} \nonumber
	\end{align}
	\caption{The single-qubit teleporter, based upon a CZ gate, a single-qubit measurement, and classical feedforward.} \label{fig:single_qubit_teleporter} \index{Single-qubit teleporter}
\end{figure}

@@

\begin{figure}[htpb]
	\includegraphics[width=0.47\textwidth]{cluster_identities} \index{Cluster state identities}
	\caption{Several cluster state identities, demonstrated in the case of linear clusters. (a) a CZ gate between two qubits creates an edge between them in the graph. (b) Measurement of a qubit in the Pauli $\hat{Y}$ basis removes that qubit from the graph, whilst creating new edges between the neighbouring qubits. (c) Measurement of a qubit in the Pauli $\hat{Z}$ basis removes that qubit and any neighbouring edges. (d) Measurement of a qubit in the Pauli $\hat{X}$ basis removes that qubit, leaving one of its neighbours as a `dangling node'.} \label{fig:cluster_ident} 
\end{figure}

>>>>

\begin{figure}[!htbp]
	\begin{align}
		\Qcircuit @C=.7em @R=.4em @! {
		\lstick{\ket{\psi_1}} & \qw & \qw & \ctrl{1} & \gate{Y} & \meter & \control \cw\\
		\lstick{\ket{\psi_2}} & \qw & \targ & \ctrl{-1} & \qw & \meter & \cwx\\
		\lstick{\ket{\psi_3}} & \gate{H} & \ctrl{-1} & \qw & \qw & \gate{X} \cwx & \gate{Z} \cwx & \rstick{\ket{\phi}} \qw
		} \nonumber
	\end{align}
	\captionspace \caption{Simple example of a quantum circuit on 3 qubits, comprising several single- and 2-qubit quantum gates and measurements. Rows represent qubits, and time flows from left-to-right.} \label{fig:eg_circuit}
\end{figure}

@@

\begin{figure}[!htbp]
	\includegraphics[width=0.3\textwidth]{cluster_state}
	\captionspace \caption{Example of a \mbox{$4\times 3$} rectangular lattice cluster state. Each vertex in the graph represents a qubit initialised into \mbox{$\ket{+}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$}. Edges represent the application of CZ gates between qubits (CZ gates commute, so the order is unimportant). Of sufficient dimension, states of this topology enable universal measurement-based quantum computation, whereby computation proceeds purely via single-qubit measurements, and all entangling operations have been commuted to the state preparation stage. Because CZ gates commute, the preparation of cluster states is time-independent, and easily implemented in a distributed or parallelised manner. The time-ordering of the single-qubit measurements is dependent on the structure of the graph and the algorithm.} \label{fig:cluster_state}
\end{figure}

@@

\begin{figure}[!htbp]
	\includegraphics[width=0.375\textwidth]{cluster_state_circuit}
	\captionspace \caption{Simple example of a cluster state that performs a computation comprising single-qubit operations and a CZ gate between two logical qubits. Let the two horizontal chains represent our two logical qubits. After inputting our input state from the left, we progressively measure out the cluster state qubits chronologically from left-to-right. Upon each single-qubit measurement, the choice of measurement basis teleports the action of a single-qubit gate. These accumulate sequentially. When we reach the point of measuring the two cluster state qubits joined with the vertical edge, the logical qubits accumulate the action of a CZ gate between them, since this is identically what that vertical edge physically corresponds to. Reaching the final two qubits, one from the upper rail and one from the lower, we obtain our two output logical qubits.} \label{fig:cluster_state_circuit}
\end{figure}

@@

\begin{figure}[!htbp]
	\begin{align}
		\Qcircuit @C=.7em @R=.4em @! {
		\lstick{\ket{\psi}} & \ctrl{1} & \gate{H} & \meter & & \\
		\lstick{\ket{+}} & \ctrl{0} & \qw & \gate{X} \cwx & \gate{H} & \rstick{\ket\psi} \qw \\
		} \nonumber
	\end{align}
	\captionspace \caption{The single-qubit teleporter, based upon a CZ gate, a single-qubit measurement, and classical feedforward.} \label{fig:single_qubit_teleporter} \index{Single-qubit teleporter}
\end{figure}

@@

\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{cluster_identities} \index{Cluster state identities}
	\captionspace \caption{Several cluster state identities, demonstrated in the case of linear clusters. (a) a CZ gate between two qubits creates an edge between them in the graph. (b) Measurement of a qubit in the Pauli $\hat{Y}$ basis removes that qubit from the graph, whilst creating new edges between the neighbouring qubits. (c) Measurement of a qubit in the Pauli $\hat{Z}$ basis removes that qubit and any neighbouring edges. (d) Measurement of a qubit in the Pauli $\hat{X}$ basis removes that qubit, leaving one of its neighbours as a `dangling node'.} \label{fig:cluster_ident} 
\end{figure}

### 2018-08-29 Sections/multi_packet_operations.tex
mdframed
Minor formatting
floats
Added quantum voting, enigma machines
Fixed caption dist

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function Transport.MultiPacketOperation(packets):
\begin{enumerate}
	\item for(packet$\in$packets) \{
	\setlength{\itemindent}{0.2in}
	\item packet.WaitFor()
	\item packet.HoldInMemory()
	\setlength{\itemindent}{0in}
	\item \}
    \item output = SomeOperation(packets.WhatOperation, packets)
    \item if(output.OperationSuccess = true) \{
	\setlength{\itemindent}{0.2in}
    \item packets.Sender.Notify(\textsc{Success})
    \item output.Costs = CombineCosts(packets.Costs)
    \item output.Attributes = \\
    CombineAttributes(packets.Attributes)
    \item return(output)
	\setlength{\itemindent}{0in}
    \item \} else \{
	\setlength{\itemindent}{0.2in}
    \item packets.Sender.Notify(\textsc{Failure})
  	\setlength{\itemindent}{0in}
    \item \}
    \item $\Box$
\end{enumerate}}}}
\caption{High-level structure of transport layer implementation of multi-packet operations.}\index{Multi-packet operations} \label{alg:trans_multi_packet}
\end{table}

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function CombineCosts.Efficiency(packets):
\begin{enumerate}
	\item costs = packets.Costs.Efficiency
	\item netCost = sum(costs)
	\item return(netCost)
    \item $\Box$
\end{enumerate}}}}
\caption{Algorithm for combining efficiency metrics in a multi-packet protocol.} \label{alg:combine_eff}
\end{table}

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function CombineCosts.Decoherence(packets):
\begin{enumerate}
	\item maxDecoherence = \\
    max(packets.Costs.Decoherence)
    \item return(maxDecoherence)
    \item $\Box$
\end{enumerate}}}}
\caption{Transport layer algorithm for combining decoherence rates in a multi-packet protocol.} \label{alg:combine_lat}
\end{table}

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function CombineCosts.Latency(packets):
\begin{enumerate}
	\item maxLatency = max(packets.Costs.Latency)
    \item return(maxLatency)
    \item $\Box$
\end{enumerate}}}}
\caption{Transport layer algorithm for combining latencies in a multi-packet protocol.} \label{alg:combine_lat}
\end{table}

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function CombineCosts.Dollars(packets):
\begin{enumerate}
	\item costs = packets.Costs.Dollars
	\item netCost = sum(costs)
	\item return(netCost)
	\item $\Box$
\end{enumerate}}}}
\caption{Transport layer algorithm for combining dollar costs in packet teleportation.} \label{alg:combine_dol}
\end{table}

>>>>

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function Transport.MultiPacketOperation(packets):
\begin{enumerate}
	\item for(packet$\in$packets) \{
	\setlength{\itemindent}{0.2in}
	\item packet.WaitFor()
	\item packet.HoldInMemory()
	\setlength{\itemindent}{0in}
	\item \}
    \item output = SomeOperation(packets.WhatOperation, packets)
    \item if(output.OperationSuccess = true) \{
	\setlength{\itemindent}{0.2in}
    \item packets.Sender.Notify(\textsc{Success})
    \item output.Costs = CombineCosts(packets.Costs)
    \item output.Attributes = \\
    CombineAttributes(packets.Attributes)
    \item return(output)
	\setlength{\itemindent}{0in}
    \item \} else \{
	\setlength{\itemindent}{0.2in}
    \item packets.Sender.Notify(\textsc{Failure})
  	\setlength{\itemindent}{0in}
    \item \}
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspace \caption{High-level structure of transport layer implementation of multi-packet operations.}\index{Multi-packet operations} \label{alg:trans_multi_packet}
\end{table}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function CombineCosts.Efficiency(packets):
\begin{enumerate}
	\item costs = packets.Costs.Efficiency
	\item netCost = sum(costs)
	\item return(netCost)
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspace \caption{Algorithm for combining efficiency metrics in a multi-packet protocol.} \label{alg:combine_eff}
\end{table}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function CombineCosts.Decoherence(packets):
\begin{enumerate}
	\item maxDecoherence = \\
    max(packets.Costs.Decoherence)
    \item return(maxDecoherence)
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspace \caption{Transport layer algorithm for combining decoherence rates in a multi-packet protocol.} \label{alg:combine_lat}
\end{table}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function CombineCosts.Latency(packets):
\begin{enumerate}
	\item maxLatency = max(packets.Costs.Latency)
    \item return(maxLatency)
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspace \caption{Transport layer algorithm for combining latencies in a multi-packet protocol.} \label{alg:combine_lat}
\end{table}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function CombineCosts.Dollars(packets):
\begin{enumerate}
	\item costs = packets.Costs.Dollars
	\item netCost = sum(costs)
	\item return(netCost)
	\item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspace \caption{Transport layer algorithm for combining dollar costs in packet teleportation.} \label{alg:combine_dol}
\end{table}

### 2018-08-29 Sections/network_algorithms.tex
Fixed caption dist

\startnormtable
\begin{table*}[!htbp]
	\begin{tabular}{|c|c|c|c|}
		\hline
  		\rowcolor{Dandelion} Algorithm & Description & Complexity class & Scaling \\
  		\hline
  		\hline
  		\rowcolor{LimeGreen} Breadth-first-search & Explore all vertices in a graph & \textbf{P} & $O(|V|+|E|)$ \\
  		\hline
  		\rowcolor{LimeGreen} Depth-first-search & (same as above) & \textbf{P} & $O(|V|+|E|)$ \\
		\hline
  		\rowcolor{LimeGreen} Shortest-path (Dijkstra) & Find the shortest route between two nodes & \textbf{P} & $O(|V|^2)$ \\
  		\rowcolor{LimeGreen} & in a directed graph & &  \\
  		  		\hline
		\rowcolor{LimeGreen} Shortest-path (\textit{A*}) & (same as above) & \textbf{P} & (varying) \\
  		  		\hline
		\rowcolor{LimeGreen} Single-source shortest path & Find the shortest paths from a given node to & \textbf{P} & $O(|V|\cdot |E|)$\\
  		\rowcolor{LimeGreen} & \textit{all} other nodes & & \\
 		\hline
		\rowcolor{LimeGreen} Minimum spanning tree & Find a spanning tree of a graph that minimises & \textbf{P} & $O(|E|\log |V|)$ \\
  		\rowcolor{LimeGreen} & the total of the edge weights & & \\
  		\hline
  		\rowcolor{LimeGreen} Minimum cost flow & Minimise total costs in a network &  \textbf{P} & $O(|V|\log |V|(|E|$\\
  		\rowcolor{LimeGreen} (Orlin) & with a specified amount of flow& & $+|V|\log |V|))$ \\
  		\hline
  		\rowcolor{LimeGreen} Maximum flow & Maximise flow in a network, regardless of costs & \textbf{P} & $O(|E|\cdot c_\mathrm{max})$ \\
  		\rowcolor{LimeGreen} (Ford-Fulkerson) & & & \\
  		\hline
  		\rowcolor{Lavender} Multi-commodity flow & Same as maximum flow, but generalised to & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & arbitrary numbers of users & (exactly), & \\
  		\rowcolor{Lavender} & & \textbf{P} (approximation & \\
  		\rowcolor{Lavender} & & using heuristics) & \\
  		\hline
  		\rowcolor{Lavender} Vehicle routing problem & Generalises the shortest-path algorithm to multiple & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & users, with distinct sources and destinations & & \\ 
  		\hline
  		\rowcolor{Lavender} Vehicle rescheduling problem & Same as above but with dynamically changing costs & \textbf{NP}-complete & ? \\
    	\hline
	\end{tabular}
	\caption{Summary of some important network algorithms and their complexities. The \textbf{NP}-complete algorithms are not believed to have efficient classical algorithms, and their exact scaling is not well understood.} \label{tab:net_alg_sum} \index{Network algorithms}\index{Breadth-first-search (BFS) algorithm}\index{Depth-first-search (DFS) algorithm}\index{Shortest-path algorithm}\index{Single-source shortest path algorithm}\index{Minimum spanning tree algorithm}\index{Minimum cost flow algorithm}\index{Maximum flow algorithm}\index{Multi-commodity flow algorithm}\index{Vehicle routing problem}\index{Vehicle rescheduling problem}
\end{table*}
\startalgtable

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[width=0.3\textwidth]{BFS_DFS_long}
	\caption{Comparison of the order in which vertices are explored, using the breadth-first-search (BFS) and depth-first-search (DFS) algorithms, where vertex 1 is the root vertex.} \label{fig:BFS_DFS}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[width=0.65\textwidth]{BFS_DFS}
	\caption{Comparison of the order in which vertices are explored, using the breadth-first-search (BFS) and depth-first-search (DFS) algorithms, where vertex 1 is the root vertex.} \label{fig:BFS_DFS}
	\end{figure*}
\fi

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function DijkstraShortestPath($G$,$A$,$B$):
\begin{enumerate}
	\item currentNode = $A$
    \item tentativeDistances[$A$] = 0
    \item tentativeDistances[others] = $\infty$
    \item nodesVisited[$A$] = True
    \item nodesVisited[others] = False
    \item loopStart:
    \item neighbours = currentNode.neighbourhood
    \item nodesVisited[neighbours] = True
    \item for(n$\in$neighbours) \{
    \setlength{\itemindent}{0.2in}
    \item newTentativeDist = \\ min(tentativeDistances[currentNode] \\+ edgeWeight[currentNode,n],\\
        tentativeDistances[n])\\
    \item nodesVisited[currentNode] = True
    \setlength{\itemindent}{0in}
    \item \}
    \item if(nodesVisited[$B$] = True) \{
    \setlength{\itemindent}{0.2in}
	\item return(tentativeDistances[$B$])
	\item $\Box$
    \setlength{\itemindent}{0in}
    \item \}
	\item currentNode = \\
	tentativeDistances[unvisitedNodes].\\
	nodeWithSmallest()
	\item goto(loop)
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\caption{Dijkstra's original shortest-path algorithm for finding the lowest weight path through a graph, $G$, between two vertices, $A$ (source) and $B$ (destination). The algorithm has $O(|V|^2)$ runtime (in \textbf{P}).} \label{alg:dijkstra}\index{Shortest-path algorithm}
\end{table}

>>>>

\startnormtable
\begin{table*}[!htbp]
	\begin{tabular}{|c|c|c|c|}
		\hline
  		\rowcolor{Dandelion} Algorithm & Description & Complexity class & Scaling \\
  		\hline
  		\hline
  		\rowcolor{LimeGreen} Breadth-first-search & Explore all vertices in a graph & \textbf{P} & $O(|V|+|E|)$ \\
  		\hline
  		\rowcolor{LimeGreen} Depth-first-search & (same as above) & \textbf{P} & $O(|V|+|E|)$ \\
		\hline
  		\rowcolor{LimeGreen} Shortest-path (Dijkstra) & Find the shortest route between two nodes & \textbf{P} & $O(|V|^2)$ \\
  		\rowcolor{LimeGreen} & in a directed graph & &  \\
  		  		\hline
		\rowcolor{LimeGreen} Shortest-path (\textit{A*}) & (same as above) & \textbf{P} & (varying) \\
  		  		\hline
		\rowcolor{LimeGreen} Single-source shortest path & Find the shortest paths from a given node to & \textbf{P} & $O(|V|\cdot |E|)$\\
  		\rowcolor{LimeGreen} & \textit{all} other nodes & & \\
 		\hline
		\rowcolor{LimeGreen} Minimum spanning tree & Find a spanning tree of a graph that minimises & \textbf{P} & $O(|E|\log |V|)$ \\
  		\rowcolor{LimeGreen} & the total of the edge weights & & \\
  		\hline
  		\rowcolor{LimeGreen} Minimum cost flow & Minimise total costs in a network &  \textbf{P} & $O(|V|\log |V|(|E|$\\
  		\rowcolor{LimeGreen} (Orlin) & with a specified amount of flow& & $+|V|\log |V|))$ \\
  		\hline
  		\rowcolor{LimeGreen} Maximum flow & Maximise flow in a network, regardless of costs & \textbf{P} & $O(|E|\cdot c_\mathrm{max})$ \\
  		\rowcolor{LimeGreen} (Ford-Fulkerson) & & & \\
  		\hline
  		\rowcolor{Lavender} Multi-commodity flow & Same as maximum flow, but generalised to & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & arbitrary numbers of users & (exactly), & \\
  		\rowcolor{Lavender} & & \textbf{P} (approximation & \\
  		\rowcolor{Lavender} & & using heuristics) & \\
  		\hline
  		\rowcolor{Lavender} Vehicle routing problem & Generalises the shortest-path algorithm to multiple & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & users, with distinct sources and destinations & & \\ 
  		\hline
  		\rowcolor{Lavender} Vehicle rescheduling problem & Same as above but with dynamically changing costs & \textbf{NP}-complete & ? \\
    	\hline
	\end{tabular}
	\captionspace \caption{Summary of some important network algorithms and their complexities. The \textbf{NP}-complete algorithms are not believed to have efficient classical algorithms, and their exact scaling is not well understood.} \label{tab:net_alg_sum} \index{Network algorithms}\index{Breadth-first-search (BFS) algorithm}\index{Depth-first-search (DFS) algorithm}\index{Shortest-path algorithm}\index{Single-source shortest path algorithm}\index{Minimum spanning tree algorithm}\index{Minimum cost flow algorithm}\index{Maximum flow algorithm}\index{Multi-commodity flow algorithm}\index{Vehicle routing problem}\index{Vehicle rescheduling problem}
\end{table*}
\startalgtable

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[width=0.3\textwidth]{BFS_DFS_long}
	\captionspace \caption{Comparison of the order in which vertices are explored, using the breadth-first-search (BFS) and depth-first-search (DFS) algorithms, where vertex 1 is the root vertex.} \label{fig:BFS_DFS}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[width=0.65\textwidth]{BFS_DFS}
	\captionspace \caption{Comparison of the order in which vertices are explored, using the breadth-first-search (BFS) and depth-first-search (DFS) algorithms, where vertex 1 is the root vertex.} \label{fig:BFS_DFS}
	\end{figure*}
\fi

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function DijkstraShortestPath($G$,$A$,$B$):
\begin{enumerate}
	\item currentNode = $A$
    \item tentativeDistances[$A$] = 0
    \item tentativeDistances[others] = $\infty$
    \item nodesVisited[$A$] = True
    \item nodesVisited[others] = False
    \item loopStart:
    \item neighbours = currentNode.neighbourhood
    \item nodesVisited[neighbours] = True
    \item for(n$\in$neighbours) \{
    \setlength{\itemindent}{0.2in}
    \item newTentativeDist = \\ min(tentativeDistances[currentNode] \\+ edgeWeight[currentNode,n],\\
        tentativeDistances[n])\\
    \item nodesVisited[currentNode] = True
    \setlength{\itemindent}{0in}
    \item \}
    \item if(nodesVisited[$B$] = True) \{
    \setlength{\itemindent}{0.2in}
	\item return(tentativeDistances[$B$])
	\item $\Box$
    \setlength{\itemindent}{0in}
    \item \}
	\item currentNode = \\
	tentativeDistances[unvisitedNodes].\\
	nodeWithSmallest()
	\item goto(loop)
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspace \caption{Dijkstra's original shortest-path algorithm for finding the lowest weight path through a graph, $G$, between two vertices, $A$ (source) and $B$ (destination). The algorithm has $O(|V|^2)$ runtime (in \textbf{P}).} \label{alg:dijkstra}\index{Shortest-path algorithm}
\end{table}
